Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-11-13 Arxiv/main.tex
update accuracy analysis

\subsubsection{Accuracy Bound for Exponential Mechanism}
\label{subsec_accuracy_global}
The accuracy bound of exponential mechanism is provided in \cite{dwork2014algorithmic} as:
\begin{equation*}
Pr[u(\expmech{}{x}{u}{\candidateset}) \leq c] 
		 \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(\dataobs)}}{2 GS})},
\end{equation*}
where $|R|$ is the size of the candidate set, $OPT$ is the optimal candidates, $|R_{OPT}|$ is the number of optimal candidates.

\subsubsection{Accuracy Bound for Laplace Mechanism}
\label{subsec_accuracy_lap}
Accuracy bound for Laplace mechanism is provided by its probability density function\cite{dwork2014algorithmic}:
$$
Pr[|Y| \geq t \cdot b] = e^{- t},
$$
where $Y \thicksim Lap(b)$, i.e.,
\begin{equation*}
Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{\Delta \bysinfer}}
\end{equation*}
in our case, where $Y \thicksim Lap(\frac{\Delta \bysinfer}{\epsilon})$.

@@

Let $\betad(\alpha, \beta)$ be the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism. By applying the probability mess function of discretized Laplace mechanism in our case with Hellinger distance, we get:
$$
\begin{array}{rcl}
& Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] 
=  \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
\end{array}
$$
where $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.\\
Also, we have:
\begin{align*}
 Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
\leq \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] 
  = \quad & Pr[ - t \leq Y < t + 1] \\
  = \quad & \frac{1}{2} (1 - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}- e^{- \frac{\epsilon t}{\Delta \bysinfer}})\\
 \end{align*}
By simplification the Hellinger distance in $\hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$, we get:

@@

  We also have:
  \begin{align*}
  & Pr\Bigg[\hellinger(\bysinfer(\dataobs), r_L )^2 
  \leq 1 - \prod_{k = 0}^{\frac{t}{2} - 1}
  \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
  \cdot
  \prod_{k = 1}^{\frac{t}{2}}
  \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}\ \Bigg] \\
  = \quad & \frac{1}{2} (1 - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}- e^{- \frac{\epsilon t}{\Delta \bysinfer}})\\
  \end{align*}

  \item[\textbf{case 2:}] \textbf{t is odd}\\
  let $t = 2 m + 1$
  \begin{align*}
   Pr\Bigg[ \hellinger(\bysinfer(\dataobs), r_L )^2 \leq & \\
  \qquad &
  1 - \frac{1}{\sqrt{1 + \frac{1}{2\alpha}}} \cdot 
  \sqrt{\frac{1}{\alpha + 2m} + \frac{- 2m - 1}{\beta(\alpha + 2m)}} \\
  \qquad &\cdot 
  \prod_{k = 0}^{m-1}
  \sqrt{(1 + \frac{1}{2(\alpha + k)})
  (1 + \frac{\frac{1}{2} - m}{(\alpha + m  + k)})
  } \\
  \qquad & \cdot 
  \prod_{k = 1}^{m} 
  \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})}\ \Bigg] \\
  \geq \quad & Pr[ - t \leq Y < t + 1] \\
  = \quad & \frac{1}{2} (1 - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}- e^{- \frac{\epsilon t}{\Delta \bysinfer}})\\
  \end{align*}

@@

\subsection{Accuracy Bound for $\hexpmech$}
\label{subsec_accuracy_smoo}
We explored following accuracy bound for $\hexpmech$:

\begin{itemize}
  \item[\textbf{lower bound}]
  \begin{align*}
  \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) \leq c} 
  = & \sum\limits_{\{r | \hellinger(\bysinfer(\dataobs), r) \leq c\}} \frac{\exp{(\frac{- \epsilon \hellinger(\bysinfer(\dataobs), r)}{4 S(\dataobs)})}}{\unomalizer{\dataobs}}\\
  \geq & \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)}})}{\unomalizer{\dataobs}}\\
  \geq & \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)}})}{|\candidateset|},
  \end{align*}

  Also, we have:
  \begin{align*}
  \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c} 
  = & \frac{2 \exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\unomalizer{\dataobs}}
  \end{align*}

  in the Bate-binomial model.\\
  Unfolding the Hellinegr distance in this accuracy bound:\\
  $c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t) = $
  \begin{align*}
  & 1 - \prod_{k = 0}^{\frac{t}{2} - 1}
  \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
  \cdot
  \prod_{k = 1}^{\frac{t}{2}}
  \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}
  \end{align*}
  when t is even, and when t is odd, let $t = 2 m + 1$:
  \begin{align*}
  \qquad &
  1 - \frac{1}{\sqrt{1 + \frac{1}{2\alpha}}} \cdot 
  \sqrt{\frac{1}{\alpha + 2m} + \frac{- 2m - 1}{\beta(\alpha + 2m)}} \\
  \qquad &\cdot 
  \prod_{k = 0}^{m-1}
  \sqrt{(1 + \frac{1}{2(\alpha + k)})
  (1 + \frac{\frac{1}{2} - m}{(\alpha + m  + k)})
  } \\
  \qquad & \cdot 
  \prod_{k = 1}^{m} 
  \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})}
  \end{align*}

>>>>

\subsubsection{Accuracy Bound for Exponential Mechanism}
\label{subsec_accuracy_global}
The accuracy bound of exponential mechanism is given in \cite{dwork2014algorithmic} as:
\begin{equation*}
Pr[u(\expmech{}{x}{u}{\candidateset}) \leq c] 
		 \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(\dataobs)}}{2 GS})},
\end{equation*}
where $|R|$ is the size of the candidate set, $OPT$ is the optimal candidates, $|R_{OPT}|$ is the number of optimal candidates.

\subsubsection{Accuracy Bound for Laplace Mechanism}
\label{subsec_accuracy_lap}
Accuracy bound for Laplace mechanism is given by its probability density function\cite{dwork2014algorithmic}:
$$
Pr[|Y| \geq t \cdot b] = e^{- t},
$$
where $Y \thicksim Lap(b)$, i.e.,
\begin{equation*}
Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{\Delta \bysinfer}}
\end{equation*}
in our case, where $Y \thicksim Lap(\frac{\Delta \bysinfer}{\epsilon})$.

@@

Let $\betad(\alpha, \beta)$ be the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$. By applying the probability mess function of discretized Laplace mechanism in our case with Hellinger distance, we get:
$$
\begin{array}{rcl}
& Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] 
=  \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
\end{array}
$$
When $\alpha = \beta$, we also have:
\begin{align*}
 Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
\leq \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] 
  = \quad & Pr[ - t \leq Y < t + 1] \\
  = \quad & \frac{1}{2} (1 - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}- e^{- \frac{\epsilon t}{\Delta \bysinfer}})\\
 \end{align*}
By simplification the Hellinger distance in $\hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$, we get:

@@

  We also have:
  \begin{align*}
  & Pr\Bigg[\hellinger(\bysinfer(\dataobs), r_L )^2 
  \leq 1 - \prod_{k = 0}^{\frac{t}{2} - 1}
  \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
  \cdot
  \prod_{k = 1}^{\frac{t}{2}}
  \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}\ \Bigg] \\
  = \quad & \frac{1}{2} (1 - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}- e^{- \frac{\epsilon t}{\Delta \bysinfer}}),
  \end{align*} 
  when $\alpha = \beta$.

  \item[\textbf{case 2:}] \textbf{t is odd}\\
  let $t = 2 m + 1$
  \begin{align*}
  Pr\Bigg[ \hellinger(\bysinfer(\dataobs), r_L )^2 = & \\
  \qquad &
  1 - \frac{1}{\sqrt{1 + \frac{1}{2\alpha}}} \cdot 
  \sqrt{\frac{1}{\alpha + 2m} + \frac{- 2m - 1}{\beta(\alpha + 2m)}} \\
  \qquad &\cdot 
  \prod_{k = 0}^{m-1}
  \sqrt{(1 + \frac{1}{2(\alpha + k)})
  (1 + \frac{\frac{1}{2} - m}{(\alpha + m  + k)})
  } \\
  \qquad & \cdot 
  \prod_{k = 1}^{m} 
  \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})}\ \Bigg] \\
  \geq \quad & Pr[ - t \leq Y < t + 1] \\
  = \quad & \frac{1}{2} (1 - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}- e^{- \frac{\epsilon t}{\Delta \bysinfer}})
  \end{align*}

  we also have: 
  \begin{align*}
   Pr\Bigg[ \hellinger(\bysinfer(\dataobs), r_L )^2 \leq & \\
  \qquad &
  1 - \frac{1}{\sqrt{1 + \frac{1}{2\alpha}}} \cdot 
  \sqrt{\frac{1}{\alpha + 2m} + \frac{- 2m - 1}{\beta(\alpha + 2m)}} \\
  \qquad &\cdot 
  \prod_{k = 0}^{m-1}
  \sqrt{(1 + \frac{1}{2(\alpha + k)})
  (1 + \frac{\frac{1}{2} - m}{(\alpha + m  + k)})
  } \\
  \qquad & \cdot 
  \prod_{k = 1}^{m} 
  \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})}\ \Bigg] \\
  \geq \quad & Pr[ - t \leq Y < t + 1] \\
  = \quad & \frac{1}{2} (1 - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}- e^{- \frac{\epsilon t}{\Delta \bysinfer}})
  \end{align*}
  when $\alpha = \beta$

@@

\subsection{Accuracy Bound for $\hexpmech$}
\label{subsec_accuracy_smoo}

\begin{definition}
\label{def_cardinality}
  $\cardinality{\dataobs}{r}$, $R^{\dataobs}_r$.

  Given $\hexpmech(\dataobs)$, define $R^{\dataobs}_r \subset \candidateset$, s.t. $r' \in R^{\dataobs}_r \iff \ux{r'} = \ux{r}$.

  Given $\hexpmech(\dataobs)$, define $\cardinality{\dataobs}{r}$ as the cardinality of $R^{\dataobs}_r$. 
\end{definition}
% \begin{itemize}
%   \item[\textbf{lower bound}]
%   \begin{align*}
%   \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) \leq c} 
%   = & \sum\limits_{\{r | \hellinger(\bysinfer(\dataobs), r) \leq c\}} \frac{\exp{(\frac{- \epsilon \hellinger(\bysinfer(\dataobs), r)}{4 S(\dataobs)})}}{\unomalizer{\dataobs}}\\
%   \geq & \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)}})}{\unomalizer{\dataobs}}\\
%   \geq & \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)}})}{|\candidateset|},
%   \end{align*}

  We have following probability distribution for accuracy:
  \begin{align}
  \label{eq_acc}
  \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c} 
  = & \frac{\cardinality{\dataobs}{c} \exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\unomalizer{\dataobs}},
  \end{align}
  $c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$, and $\cardinality{\dataobs}{c} = 2$ when $t \neq 0$.\\
  Unfolding the Hellinegr distance in this accuracy bound:

 \begin{itemize}

  \item[\textbf{case 1:}] \textbf{t is even}

  \begin{align*}
  &\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z)^2 =  1 - \prod_{k = 0}^{\frac{t}{2} - 1}
  \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
  \cdot
  \prod_{k = 1}^{\frac{t}{2}}
  \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}\ }\\
  = & \frac{2 \exp{(\frac{- \epsilon \sqrt{1 - \prod_{k = 0}^{\frac{t}{2} - 1}
  \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
  \cdot
  \prod_{k = 1}^{\frac{t}{2}}
  \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}}}{4 S(\dataobs)})}}{\unomalizer{\dataobs}}
  \end{align*}

  \item[\textbf{case 2:}] \textbf{t is odd}

  \begin{align*}
  c^2 = \qquad &
  1 - \frac{1}{\sqrt{1 + \frac{1}{2\alpha}}} \cdot 
  \sqrt{\frac{1}{\alpha + 2m} + \frac{- 2m - 1}{\beta(\alpha + 2m)}} \\
  \qquad &\cdot 
  \prod_{k = 0}^{m-1}
  \sqrt{(1 + \frac{1}{2(\alpha + k)})
  (1 + \frac{\frac{1}{2} - m}{(\alpha + m  + k)})
  } \\
  \qquad & \cdot 
  \prod_{k = 1}^{m} 
  \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})}
  \end{align*}
  Substitute the $c$ in Equation, (\ref{eq_acc})
